---
title: "ORCID_basic"
format: html
editor: visual
---

# ORCID Data Visualization - Basic

## Set variables

### Organization identifiers for use in ORCID API

add info on getting identifiers

```{r organization ids}
ringgold_id <- "7017" 
grid_id <- "grid.260288.6" 
ror_id <- "https://ror.org/03grc6f14"
# instructions on formatting email domain
email_domain <- "@mta.ca" 
organization_name <- "Mount Allison University"
```

### Location information for geonames web services and map creation

add info on setting up Geonames and enabling web services

```{r}
options(geonamesUsername = "estregger")
anchor_org<-"Mount Allison University"
anchor_city<-"Sackville"
anchor_region<-"New Brunswick"
anchor_country<-"Canada"
home_city <- anchor_city
home_country <- anchor_country

```

### Set filters used in code file

```{r set filters}
# set start year in YYYY format
my_year = 2018
# set organization keyword for filtering possible matches
my_org_keyword = "Mount Allison"
```

## Run code file 

add info on changing default options

add info on data cleaning

add estimated run time

Expect warnings

```{r run Rorcid Crossref Authors}
source("./Rorcid_Crossref_Authors.R")
```
